\documentclass[a4paper]{article}
\usepackage{amsmath}

\title{Computing For Mathematics: Projectile Motion Of Darts}
\author{Luke Sargent, Matthew Squire, Cameron Trew, Aron Russell}

\begin{document}
\maketitle

\section{Introduction}
This project has an extremely trivial goal. Simply input 3 values relating to the throw of a dart
- tilt angle, swivel ange and initial velocity. Then output the score of which is obtained, along with the
relevant statistics. This project involves many areas of mathematics to solve.
Primarily Mechanics and Geometry.


\begin{itemize}\label{Glossary Of Terms}
    \item \(\theta_\tau = Tilt angle from the horizontal, upwards\)
    \item \(\theta_\sigma = Swivel angle from vertical, to the right/clockwise\)
    \item \(R_x = Range Of Dart (in x direction)\)
    \item \(H_y = Height Of Dart (in y direction)\)
\end{itemize}

\section{Statement Of Need}

\section{State Of The Field}

\section{Phase I - Projectile In 2D}
We must first consider the 2-dimensional plane (x,y) in which our dart
travels through. Doing, we can model the trajectory of the dart using projectile motion
in order to obtain the range, height, and shift of the dart.We can say that air resistance of the dart is negligible.This can be done using the following equations:

\begin{align}
    R_x & = \frac{v_0sin(2\theta_\tau)}{2g}\\
    H_y & = (Range_x)tan(\theta_\tau) - \frac{g(Range_x)^2}{2v_0cos{\theta_\tau}^2}\\
    Shift_z & = \pm\sqrt{(Range_x)^2 - (x_0 - Board)^2}
\end{align}

\section{Phase II - Geometry Of Dartboard}
Determining the score is precisely the same as determining the position at which the dart landed
on the dartboard. Since we are going to obtain a position of the dart in polar form r, theta, we can
replicate the techniques used to determine the modulus and argument of a complex number.
However instead of being given a real and imaginary part, we are given a length in the y and z direction.
Taking the bullseye to be the centre of origin, we apply the following to calculate r and theta:
    
\end{document}